Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-10 doc/paper.tex
update

 We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{MinArea} instances:\fxnote{TODO:Milan: main characteristics, why they differ from others}
     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set. In overall, we have 194 polygons. 
	We included two kind of weights into each of (194) polygons:
	\begin{itemize}
		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$. Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$. This implies that the spectrum of camera installed at $v_i$ has to be larger, which implies that it should be of a higher quality, i.e,. a higher price. In case that we have the second edge begin smaller, we consider arithmetic mean of the both lengths as the weight of the vertex.
		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this, we assign prices to each vertex on the following way:
		\begin{equation}
		w_i = n \cdot \frac{|V(i)|}{|D(P)|}, i=1,...,n.
		\end{equation}
	\end{itemize}

@@

         Summarized numerical results for all of our algorithm variants are displayed in Table~\ref{tab: t_w0} and Table~\ref{tab: t_w1} for topollogically-based benchmarks and point-based benchmarks, respectively. Each of the tables is additionally  subdivided by a vertical line into two parts, depending on the case if we consider \emph{small} or \emph{large} polygons for a specific weight.
         For each of the algorithm  we reported average quality and average standard deviation ($\sigma$) over all instances (96 instances) of the considered subgroup. If an asterisk is given, i means taht optimality is proven for all instances of considered subgroup.

     \begin{table}[]
     	\centering
     	 \scalebox{0.85}{
     	\begin{tabular}{l|lllllll}    \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 15.93  & 0.15    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.22   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 22.63  & 0.00    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & 0.00    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.07    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.00    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
     	\end{tabular}}
        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}
     \end{table}

      \begin{table}[]
      	\centering
      	\scalebox{0.85}{
      	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & 36.03  & 0.00    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & 36.03  & 18.95   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Greedy-1}             & 39.28  & 0.00    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & 0.00    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.01    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.00    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
      	\end{tabular}}
         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}
      \end{table}

     \begin{table}[]
      \centering
       \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & 2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
     	\end{tabular}}
          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.}
     \end{table}

    \begin{table}[]
    	\centering
    	\scalebox{0.85}{
 	  \begin{tabular}{l|lllllll} \hline
 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & 6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & 6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		   \textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
 		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}}
    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}
   \end{table}

        From the numerical results, we observe the following conclusions:
        \begin{itemize}
        	\item  For the topollogically--based benchmarks and the exact approaches, \textsc{Cplex} achieved best results among other approaches. moreover, \textsc{Cplex} could prove optimallity of all (192) instances, while \textsc{Cp} could not. It is expecially noticed for small polygons, where it seems hard for \textsc{Cp} to prove optimality.
        	\item For the point--based benchmark set and the exact approaches, \textsc{Cplex} again show its power, since it could prove all instances to optimallity, which is also the case of \textsc{Cp}.
        	\item  For the topollogically--based benchmarks and the heuristic approaches\fxnote{TODO...}
        \end{itemize}
          \fxnote{TODO: Milan: generisati plotove za vremena svakog od algoritama, takodje generisati plotove koji pokazuju procenat pokrivenosti optimalnih rjesenja CPLEX-a...}

	\section{Conclusions and Future Work}

>>>>

 We used two different kind of benchmark sets:
     \begin{itemize}
     	 \item \emph{MinArea} instances:\fxnote{TODO: Milan: main characteristics, why they differ from others}
     	 \item \emph{FAT} instances: \fxnote{TODO: Milan: main characteristics, why they differ from others}
     \end{itemize}
     For \emph{MinArea} and \emph{FAT} instances, one polygon for each $n \in\{8,10,...,200\}$ has been generated, which makes 97 instances per each benchmark set. In overall, we have 194 polygons. 
	We included two kind of weights into each of (194) polygons:
	\begin{itemize}
		\item \emph{topologically-based related weights} ($W0$): For each vertex $v_i$ of polygon $P$ we denote by $l_i$ and $l_{i+1}$ the lengths of two edges that come out of the vertex $v_i$. Then, we set $w_i := \frac{l_i + l_{i+1}}{2}$. This way of assigning weights is augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that a guard can see a larger pieces of polygon $P$. This implies that the spectrum of camera installed at $v_i$ has to be larger, which implies that it should be of a higher quality, i.e,. a higher price. In case that we have the second edge begin smaller, we consider arithmetic mean of the both lengths as the weight of the vertex.
		\item \emph{point-based related weights} ($W1$): For each vertex $j$, we consider the number of points in $D(P)$ that are visible from the given vertex $(|V(j)|)$. Based on this, we assign prices to each vertex on the following way:
		\begin{equation}
		w_i = n \cdot \frac{|V(i)|}{|D(P)|}, i=1,...,n.
		\end{equation}
	\end{itemize}

@@

         Summarized numerical results for each of our 6 variants of our algorithm are displayed 
         in Tables~\ref{small_w0} --\ref{large_w1}. For each table, the average results are reported for each subset of instances grouped w.r.t. a specific kind of instances and a specific weight (97 instances per each group). Each of the tables list the considered algorithms in the first column. Starting with column two,  each of the lines provide detailed statistics for respective algorithm.  The statistics report: the average solution quality ($\bar{|s|}$), the average time ($\bar{t}[s]$), the average number of guards which are included in each of the solutions ( $\bar{|g|}$), the number of solutions which match to the optimum solutions (\#hitsMinH), standard deviation of the obtained solutions w.r.t. optimal solutions ($\sigma(Opt)$), then the number of minimal solutions w.r.t. the four heuristics achieved by the respective algorithm (\#hitsMinH), standard deviation w.r.t. best solutions achieved by the four heuristic algorithms   ($\sigma(MinH)$).

     \begin{table}[]
     	\centering
     	 \scalebox{0.83}{
     	\begin{tabular}{l|lllllll}    \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & *15.93  & 0.152    & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & 16.04  & 98.215   & 18.96     & 67/97     & 0.02    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 22.63  & 0.002    & 26.28     & 0/97      & 0.79    & 3/97       & 7.61     \\
     		\textsc{Greedy-2}          & 19.97  & 0.002    & 20.14     & 0/97      & 0.44    & 0/97       & 0.20     \\
     		   \textsc{Greedy-1+Cplex}  & 18.49  & 0.073    & 21.19     & 2/97      & 0.30    & 57/97      & 0.06     \\
     		   \textsc{Greedy-2+Cplex} & 18.39  & 0.004    & 19.59     & 0/97      & 0.26    & 53/97      & 0.04  \\ \hline 
     	\end{tabular}}
        \caption{The results on the benchmark set $MinArea$ for the type of weight $W0$.}\label{small_wo}
     \end{table}

      \begin{table}[]
      	\centering
      	\scalebox{0.83}{
      	\begin{tabular}{l|lllllll} \hline
      		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &  $ \bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
      		\textsc{Cplex}            & *36.03  & 0.003   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Cp}               & *36.03  & 18.953   & 18.93     & 97/97     & 0.00    & N/A        & N/A      \\
      		\textsc{Greedy-1}             & 39.28  & 0.001    & 20.15     & 2/97      & 0.35    & 4/97       & 0.24     \\
      		\textsc{Greedy-2}          & 40.92  & 0.001    & 20.96     & 0/97      & 0.51    & 0/97       & 0.40     \\
      		   \textsc{Greedy-1+Cplex}  & 37.78  & 0.006    & 19.41     & 4/97      & 0.21    & 19/97      & 0.08     \\
      		   \textsc{Greedy-2+Cplex} & 37.31  & 0.003    & 19.58     & 2/97      & 0.15    & 81/97      & 0.19   \\ \hline  
      	\end{tabular}}
         \caption{The results on the bemchmark set $MinArea$ for the  type of weight $W1$.}\label{small_w1}
      \end{table}

     \begin{table}[]
      \centering
       \scalebox{0.85}{
     	\begin{tabular}{l|lllllll} \hline
     		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ &optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
     		\textsc{Cplex}            & *2.62   & 0.02    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Cp}               & *2.62   & 8.17    & 7.32      & 97/97     & 0.00    & N/A        & N/A      \\
     		\textsc{Greedy-1}             & 3.39   & 0.35    & 7.81      & 0/97      & 0.09    & 23/97      & 0.05     \\
     		\textsc{Greedy-2}          & 3.52   & 0.32    & 6.61      & 2/97      & 0.10    & 28/97      & 0.08     \\
     		   \textsc{Greedy-1+Cplex}  & 3.34   & 0.35    & 8.91      & 4/97      & 0.08    & 25/97      & 0.04     \\
     		   \textsc{Greedy-2+Cplex} & 3.32   & 0.33    & 6.81      & 6/97      & 0.08    & 25/97      & 0.04  \\ \hline   
     	\end{tabular}}
          \caption{The results on the benchmark set $FAT$ for the type of weight $W0$.} \label{largel_wo}
     \end{table}

    \begin{table}[]
    	\centering
    	\scalebox{0.85}{
 	  \begin{tabular}{l|lllllll} \hline
 		Alg.           & $\bar{|s|}$ & $\bar{t}[s]$ &   $\bar{|g|}$ & optHit & $\sigma(Opt)$ & \#hitsMinH & $\sigma(MinH)$ \\ \hline
 		\textsc{Cplex}            & *6.72   & 0.02    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Cp}               & *6.72   & 0.36    & 6.44      & 97/97     & 0.00    & N/A        & N/A      \\
 		\textsc{Greedy-1}             & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		\textsc{Greedy-2}          & 6.77   & 0.31    & 6.49      & 92/97     & 0.02    & 92/97      & 0.04     \\
 		   \textsc{Greedy-1+Cplex}  & 6.73   & 0.32    & 6.45      & 96/97     & 0.01    & 96/97      & 0.03     \\
 		   \textsc{Greedy-2+Cplex} & 7.42   & 0.31    & 6.46      & 90/97     & 0.33    & 92/97      & 0.33    \\ \hline
 	\end{tabular}}
    \caption{The results on the benchmark set $FAT$ for the type of weight $W1$.}\label{small_w1}
   \end{table}

        From the numerical results, we observe the following conclusions concerning exact solving:
        \begin{itemize}
        	\item  \textsc{Cplex} could solve all solution to prove optimality within a fraction of a second;
        	\item   \textsc{Cp} was able to solve all those instances with weight $W1$ but with signifficanlty more time than required from \textsc{Cplex};
        	\item For the subset of instances $MinArea$ which includes weight $W0$, the performance of Cp degrades signifficantly which can be seen  by the respective avg. runtime and the number of optimal solutions found (67/97).
        \end{itemize}
     From the numerical results, we observe the following conclusions concerning heuristic solving:
     \begin{itemize}
     	\item \fxnote{TODO...}
     \end{itemize}
	\section{Conclusions and Future Work}
